Simulation Study: Varying Null Proportion

### 2018-08-09 datasets/simulations/simulations-varyinginformativeness.Rmd
Remove 'lowsignal' from file names, not running 2 signal levels

## intermediary files we create below
info00_file <- file.path(resdir, "varyinginfo-lowsignal-benchmark-level00.rds")
info20_file <- file.path(resdir, "varyinginfo-lowsignal-benchmark-level20.rds")
info40_file <- file.path(resdir, "varyinginfo-lowsignal-benchmark-level40.rds")
info60_file <- file.path(resdir, "varyinginfo-lowsignal-benchmark-level60.rds")
info80_file <- file.path(resdir, "varyinginfo-lowsignal-benchmark-level80.rds")
info100_file <- file.path(resdir, "varyinginfo-lowsignal-benchmark-level100.rds")

>>>>

## intermediary files we create below
info00_file <- file.path(resdir, "varyinginfo-benchmark-level00.rds")
info20_file <- file.path(resdir, "varyinginfo-benchmark-level20.rds")
info40_file <- file.path(resdir, "varyinginfo-benchmark-level40.rds")
info60_file <- file.path(resdir, "varyinginfo-benchmark-level60.rds")
info80_file <- file.path(resdir, "varyinginfo-benchmark-level80.rds")
info100_file <- file.path(resdir, "varyinginfo-benchmark-level100.rds")

### 2018-08-09 datasets/simulations/simulations-varyingntests.Rmd
Remove 'lowsignal' from file names, not running 2 signal levels

## intermediary files we create below
n100_file <- file.path(resdir, "varyingntests-lowsignal-benchmark-n100.rds")
n500_file <- file.path(resdir, "varyingntests-lowsignal-benchmark-n500.rds")
n1000_file <- file.path(resdir, "varyingntests-lowsignal-benchmark-n1000.rds")
n5000_file <- file.path(resdir, "varyingntests-lowsignal-benchmark-n5000.rds")
n10000_file <- file.path(resdir, "varyingntests-lowsignal-benchmark-n10000.rds")
n50000_file <- file.path(resdir, "varyingntests-lowsignal-benchmark-n50000.rds")

>>>>

## intermediary files we create below
n100_file <- file.path(resdir, "varyingntests-benchmark-n100.rds")
n500_file <- file.path(resdir, "varyingntests-benchmark-n500.rds")
n1000_file <- file.path(resdir, "varyingntests-benchmark-n1000.rds")
n5000_file <- file.path(resdir, "varyingntests-benchmark-n5000.rds")
n10000_file <- file.path(resdir, "varyingntests-benchmark-n10000.rds")
n50000_file <- file.path(resdir, "varyingntests-benchmark-n50000.rds")

### 2018-08-09 datasets/simulations/simulations-varyingpi0.Rmd
Remove 'lowsignal' from file names, not running 2 signal levels

## intermediary files we create below
null05_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop05.rds")
null10_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop10.rds")
null20_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop20.rds")
null30_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop30.rds")
null40_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop40.rds")
null50_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop50.rds")
null60_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop60.rds")
null70_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop70.rds")
null80_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop80.rds")
null90_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop90.rds")
null95_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop95.rds")
null99_file <- file.path(resdir, "varyingpi0-lowsignal-benchmark-nullprop99.rds")

>>>>

## intermediary files we create below
null05_file <- file.path(resdir, "varyingpi0-benchmark-nullprop05.rds")
null10_file <- file.path(resdir, "varyingpi0-benchmark-nullprop10.rds")
null20_file <- file.path(resdir, "varyingpi0-benchmark-nullprop20.rds")
null30_file <- file.path(resdir, "varyingpi0-benchmark-nullprop30.rds")
null40_file <- file.path(resdir, "varyingpi0-benchmark-nullprop40.rds")
null50_file <- file.path(resdir, "varyingpi0-benchmark-nullprop50.rds")
null60_file <- file.path(resdir, "varyingpi0-benchmark-nullprop60.rds")
null70_file <- file.path(resdir, "varyingpi0-benchmark-nullprop70.rds")
null80_file <- file.path(resdir, "varyingpi0-benchmark-nullprop80.rds")
null90_file <- file.path(resdir, "varyingpi0-benchmark-nullprop90.rds")
null95_file <- file.path(resdir, "varyingpi0-benchmark-nullprop95.rds")
null99_file <- file.path(resdir, "varyingpi0-benchmark-nullprop99.rds")
